---
title: "MyshinyApp"
author: "Bence Szikora"
date: "2025-03-11"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The data

This presentation contains the main information for myShinyApp.

The data set of the app is the diamond data set from the ggplot2 package. This data set contains the prices and other attributes of almost 54,000 diamonds.

Here is the head of the data set:

```{r}
library(ggplot2)
head(diamonds)
```

## How to use the app

This application  can help yo to estimate the price (USD) of your diamond with a given weight (carat) based on your diamond type.

You can select:

- the quality of the cut  
- the color of your diamond (D is the most valuable, J is the least)
- the weight of your diamond (with 0.1 step)

## The code:
The code for the plot in the next slide:

```{r, echo=TRUE, results='hide'}
#data=diamonds
#data1 <- data[data$cut == "Fair" & data$color == "D", ]
#d=plot(data1$carat, data1$price, pch = 19, 
#                 xlab = "Carat",
#                 ylab = "Price",
#                 main = paste("Price per carat for Fair cut and D color"),
#                 xlim = c(0, 5), ylim = c(0, 20000))

```

## A demo plot from the app.

```{r}
data=diamonds
data1 <- data[data$cut == "Fair" & data$color == "D", ]
plot(data1$carat, data1$price, pch = 19, 
                 xlab = "Carat",
                 ylab = "Price",
                 main = paste("Price per carat for Fair cut and D color"),
                 xlim = c(0, 5), ylim = c(0, 20000))
```

